{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-11 paper/paper.tex
renamed section discussion to summary
corrected spelling
added explanation of the structure of the paper

The idea of Barthe et. al. was to close this channel by compiling
type information into the byte-code, which cause the scheduler to
treat the secure parts in a different way. The fact that many mobile
platforms already use some byte-code (e.g. Android a modification
of the JVM byte-code) may have been a reason for the decision to use
type-annotated byte-code.

\section{Introduction to research area}
\label{sec:introduction}
\section{Discussion of the paper}
\label{sec:discussion}
\subsection{Syntax and Semantics of multithreaded programs}
\label{sec:syntaxsemantics}
\subsection{Type system}
\label{sec:typesystem}
\subsection{Soundness}
\label{sec:soundness}
\subsection{Instantiation}
\label{sec:instantiation}

>>>>

The idea of Barthe et. al. was to close this channel by compiling
type information into the byte-code, which cause the scheduler to
treat the secure parts in a different way. The fact that many mobile
platforms already use some byte-code (e.g. Android uses a modification
of the JVM byte-code) may have been a reason for the decision to use
type-annotated byte-code.

\section{Introduction to research area}
\label{sec:introduction}
\section{Summary of the article}
\label{sec:discussion}
In this summary I will follow mainly the structure of the original
paper which is as follows. After the introduction the basic terms and
definitions for a multithreaded programs and the scheduler are laid.
After that the notion of security we want to achieve is presented. Along
with this a skeleton of a type system is described, which ensures that a
program typable in this type system is secure w.r.t the notion of security.
The proof that this holds is sketched in the following section. In the
last section the (by now) abstract framework is instantiated with a
concrete example.

\subsection{Syntax and Semantics of multithreaded programs}
\label{sec:syntaxsemantics}
\subsection{Type system}
\label{sec:typesystem}
\subsection{Soundness}
\label{sec:soundness}
\subsection{Instantiation}
\label{sec:instantiation}
